\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    margin=0.65in,
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{153, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage[
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage{ragged2e}

% Settings
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

% Title format
\titleformat{\section}{\bfseries\normalsize\color{primaryColor}}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{0pt}{*1.3}{*0.4}

% Custom bullet format
\renewcommand\labelitemi{\small\textbullet}
\newenvironment{highlights}{
    \begin{itemize}[
        topsep=1.5pt,
        parsep=0pt,
        partopsep=0pt,
        itemsep=1.5pt,
        leftmargin=10pt
    ]
}{
    \end{itemize}
}

% Save space - make links without arrows
\let\hrefWithoutArrow\href
\renewcommand{\href}[2]{\hrefWithoutArrow{#1}{#2}}

\begin{document}

% HEADER
\begin{center}
\textbf{\LARGE \color{primaryColor}PHAM HOANG NAM}\\[5pt]
\small District 7, HCM City, Vietnam \ | \
\href{mailto:hoangnampham3103@gmail.com}{hoangnampham3103@gmail.com} \ | \
+84 0856782768 \ | \
\href{https://github.com/HwanNorm}{GitHub} \ | \
\href{https://www.linkedin.com/in/pham-hoang-nam-aa370b309/}{LinkedIn}
\end{center}

\vspace{4pt}

% PROFESSIONAL EXPERIENCE
\section{PROFESSIONAL EXPERIENCE}

\textbf{AI Research Engineer Intern --- Bach Khoa Computer Engineering (Dien Toan Group)} \hfill \textit{Mar – Jun 2026}
\begin{highlights}
\item Built a text-based person search system over 214,000+ images using fine-tuned CLIP (ViT-B/16), enabling natural language queries like ``man in blue jacket'' to retrieve matching person images.
\item Designed a two-stage retrieval pipeline combining fast vector search (Qdrant) with GPU reranking to improve result precision.
\item Surveyed state-of-the-art text-based person re-identification research, comparing model architectures and benchmarking on standard metrics (R@1, R@5, mAP).
\item Deployed full-stack demo: FastAPI backend with query caching, React frontend, GPU inference on Colab via ngrok.
\end{highlights}

\vspace{6pt}

\textbf{AI Engineer Intern --- WATA Software (Ho Chi Minh City)} \hfill \textit{Sep – Dec 2025}
\begin{highlights}
\item Built automated medical data ingestion pipeline using Docling + Crawl4AI to convert PDFs and clinical texts into structured formats, with Supabase storage integration for document management.
\item Created a custom healthcare NER model to extract drugs, diseases, and dosages, improving retrieval accuracy.
\item Integrated OpenFDA Drug API to deliver safe, validated medication information for chatbot responses.
\item Modified LangGraph state management and LangChain schemas to incorporate new features into agent workflow.
\item Developed agent nodes for LangGraph workflow including intent routing logic and medical-specific retrieval strategies.
\item Collaborated on Docker deployment and LangSmith/LangFuse integration for agent tracing and monitoring.
\end{highlights}

\vspace{6pt}

% PROJECTS
\section{PROJECTS}

\noindent
\textbf{Credit Default Risk Modeling (Home Credit Dataset)} \small{[\href{https://github.com/HwanNorm/Home-Credit-Default-Risk-Prediction}{GitHub}] [\href{https://huggingface.co/spaces/CodexN/Home-Credit-Default-Risk}{Live Demo}]} \hfill \textit{Aug – Sep 2025}
\begin{highlights}
\item Analyzed 300,000+ loan applications across 7 datasets performing comprehensive EDA to identify risk patterns: lower education and unstable employment correlated with higher default rates. Engineered 200+ time-based features capturing payment behavior and credit utilization. Benchmarked 6 ML algorithms achieving ROC-AUC 0.77 with 12\% improvement over baseline. Built demo web app using FastAPI and Docker deployed on Hugging Face Spaces.
\item \textbf{Technologies:} Python, Pandas, NumPy, Scikit-learn, LightGBM, XGBoost, CatBoost, Statistical Analysis, FastAPI, Docker
\end{highlights}

\vspace{4pt}

\noindent
\textbf{Bank Marketing Campaign Optimizer} \small{[\href{https://github.com/HwanNorm/Bank-Marketing-Campaign-Optimizer}{GitHub}]} \hfill \textit{Jul 2 - Jul 28 2025}
\begin{highlights}
\item Developed ML model to optimize bank marketing campaigns achieving 3.8x lift in customer targeting efficiency. Performed comprehensive EDA on banking dataset, built logistic regression classifier with 73\% ROC-AUC, and created vintage analysis framework. Generated actionable business recommendations for marketing optimization and resource allocation.
\item \textbf{Technologies:} Python, Pandas, Numpy, Scikit-learn, Matplotlib, Seaborn
\end{highlights}

\vspace{4pt}

\noindent
\textbf{Stock Market Prediction System} \small{[\href{https://github.com/HwanNorm/Stock-Market-Prediction-System}{GitHub}]} \hfill \textit{Sep - Nov 2024}
\begin{highlights}
\item Built LSTM-based stock price prediction system analyzing 3,000+ companies across NASDAQ and Vietnamese markets. Engineered robust data pipeline to handle compressed archives and process gigabytes of financial data, developed automated trading signal system for identifying optimal buy/sell opportunities, and created investment portfolio optimization achieving 18.90\% expected returns with low risk.
\item \textbf{Technologies:} Python, TensorFlow, Pandas, Scikit-learn, NumPy, Big Data Processing, Time Series Analysis
\end{highlights}

\vspace{8pt}

% TECHNICAL SKILLS
\section{TECHNICAL SKILLS}

\noindent
\textbf{Languages:} Python, Java, SQL, R\\[3pt]
\textbf{Data Science \& Analytics:} EDA, Statistical Analysis, Hypothesis Testing, Feature Engineering, Data Visualization (Matplotlib, Seaborn, Plotly), Machine Learning, Deep Learning, Predictive Modeling, Big Data Processing, Time-series Analysis\\[3pt]
\textbf{ML Frameworks \& Libraries:} Scikit-learn, Pandas, NumPy, XGBoost, LightGBM, CatBoost, PyTorch, TensorFlow, Keras\\[3pt]
\textbf{AI \& LLMs:} Agentic RAG Systems, LangGraph, LangChain, Tool-Use Agents, NLP, Prompt Engineering, Vector Search, NER\\[3pt]
\textbf{Engineering \& Deployment:} FastAPI, Flask, RESTful APIs, Docker, Git, LangSmith/LangFuse, Node.js, React (basic)

\vspace{8pt}

% EDUCATION
\section{EDUCATION}

\noindent
\textbf{Fulbright University Vietnam} \hfill \textit{2022 – 2026}\\
Bachelor of Science in Computer Science \hfill GPA: 3.14/4.0\\[3pt]

\noindent
\textbf{Languages:}\\
• Vietnamese (Native)\\
• English (Fluent --- IELTS 7.0)

\end{document}
